Explore consensus cell types

### 2025-01-24 analyses/cell-type-consensus/exploratory-notebooks/02-explore-consensus-results.Rmd

    project_df <- plot_df |> 
      dplyr::filter(project_label == {{label}}) |> 
      dplyr::mutate(
        # relevel factors for specific project 
        top_celltypes = forcats::fct_infreq(top_celltypes) |> 
          forcats::fct_relevel("All remaining cell types", "Unknown", after = Inf)
      )

>>>>

    project_df <- plot_df |> 
      dplyr::filter(project_label == label) |> 
      dplyr::mutate(
        # relevel factors for specific project 
        top_celltypes = forcats::fct_infreq(top_celltypes) |> 
          forcats::fct_relevel("All remaining cell types", "Unknown", after = Inf)
      )
